The Next Release Problem in Real World

### 2018-12-18 PaperBody.tex
Updates from ShareLaTeX

\textbf{RQ2}. \textit{Could we estimate COST from Bugzilla without Forward Looking?}
\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{images/boxplotraw.png}
    \caption{Priority-number of comments}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{images/boxplot.png}
    \caption{Priority-Log(number of comments)}
  \end{subfigure}
  \caption{The same cup of coffee. Two times.}
  \label{fig:priority_comments}
\end{figure*}
\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{images/chart_ec.png}
    \caption{Eclipse}
  \end{subfigure}
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{images/chart_ff.png}
    \caption{Firefox}
  \end{subfigure}
  \caption{Average Time cost at 2016 and 2017 per components}
  \label{fig:time_cost}
\end{figure*}
\subsection{Profit}

@@

 To find out, we compared the actual Priority to the Number of Comments. Figure 1.(a) shows this as a box plot. The higher the priority, the more the comment. However, you can see that there are too many outliers and that the data is distributed asymmetrically. This is because the number of comments follows a log distribution. So we applied the logarithmic function to the number of commands and then we compared it again. This is shown in Figure 1.(b)

As Figure 1.(b) shows, Priority and Member of Comments have a linear relationship. Unlike Priority, Number of segments has a constant distribution of values and various values by requirement. Number of Comments is better than Priority to apply the actual search-based algorithm.

@@

 Unlike Profit, the Cost was a very difficult task to figure out the actual prediction. In fact, it's very difficult for a product manager to calculate the time cost of a particular requirement, and the developers working on the actual task are just guessing how much time they'll take. 
 So we defined the Cost as:

Cost: Average resolution time for the requirements of the same component as the previous year

Bugzilla's repositories are divided into each component. We assumed that the average time it takes to fix the bug for each component would be a constant in next year. Therefore, We concluded that the average bug modification time for each component in 2017 would not be much different from 2016. So the Cost of each requirement was used as a prediction index for the average Cost of that component in 2016.

@@

\caption{Profit Comparison for each dataset}
\label{fig:DatasetProfit}
\end{figure*}

@@

At second experiment(EX2), we applied each algorithm to \textit{FIREFOX-III} dataset to analyze the correlation between cost and profit. And also, we expected to get the interesting range which have a great change as the limited budget are increased or decreased.\\

@@

\section{Result and Analysis}

@@

\begin{table*}[t]
\caption{Profit on each limited budget}
\begin{tabular}{@{}crrrrr@{}}
\toprule
\multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}The limited\\ budget\end{tabular}}} & \multicolumn{5}{c}{Algorithms}                                                                                                    \\ \cmidrule(l){2-6} 
\multicolumn{1}{c}{}                                                                              & \multicolumn{1}{c}{AHP} & \multicolumn{1}{c}{ILP} & \multicolumn{1}{c}{SA} & \multicolumn{1}{c}{GA} & \multicolumn{1}{c}{NSGA-II} \\ \midrule
100,000 & 14472.21303& \textbf{14530.92923}& 13787.94014& 13916.62496& 14359.51809\\
120,000 & 16798.95935& \textbf{16845.48739}& 16269.28033& 16440.60658& 16746.14339\\
140,000 & 18948.34660& \textbf{18979.35023}& 18553.36746& 18706.04924& 18906.95215\\
160,000 & 20906.31785& \textbf{20934.94744}& 20559.69749& 20656.69427& 20873.08535\\
180,000 & 22683.10701& \textbf{22718.92665}& 22332.52554& 22449.04724& 22651.51132\\
200,000 & 24343.18852& \textbf{24369.86106}& 23894.25792& 24054.60654& 24281.04096\\
220,000 & 25881.18360& \textbf{25901.23028}& 25425.18545& 25565.45349& 25804.51079\\
240,000 & 27305.09756& \textbf{27324.51067}& 26790.58789& 26987.08126& 27214.27095\\
260,000 & 28626.58769& \textbf{28653.54334}& 28161.56720& 28293.21833& 28556.63614\\ \bottomrule
\end{tabular}
\label{table:ParetoFront}
\end{table*}

\subsection{Experiment 1}
At EX1, we applied two deterministic and three heuristic algorithms to four datasets and compared the averaged maximum profit to each other. Figure \ref{fig:DatasetProfit} shows the results of EX1. Each graph expresses the profit of five algorithms under the limited budget(= the estimated cost).

The SA has the smallest profit in most cases, except Figure \ref{fig:DatasetProfit}-(c). Although the SA started from a greedy solution, there is little difference between the result and a greedy solution. The profit of GA is bigger than SA and smaller than NSGA-II in every cases. So, the profit is high in order of NSGA-II, GA, then SA. The AHP has good performances for some cases. However, it has the lowest profit in \ref{fig:DatasetProfit}-(c). Therefore, we can conclude that the strategy about evaluating profit can be affect the results.

The run time of two deterministic algorithms were much faster than heuristic algorithms. Therefore, we can conclude that the ILP is well-suited for our datasets and also it is much faster than other heuristic algorithms.

\subsection{Experiment 2}

One of the reasons to perform EX2 was that we wondered if there is a peculiar part in cost-profit graph. However, we cannot observe prominently peculiar part in the dataset.

>>>>

\textbf{RQ2}. \textit{Could we estimate COST from Bugzilla without Forward Looking?}

\subsection{Profit}

@@

 To find out, we compared the actual Priority to the Number of Comments. Figure n shows this as a box plot. The higher the priority, the more the comment. However, you can see that there are too many outliers and that the data is distributed asymmetrically. This is because the number of comments follows a log distribution. So we applied the logarithmic function to the number of commands and then we compared it again. This is shown in Figure n+1.

As Figure shows, Priority and Member of Comments have a linear relationship. Unlike Priority, Number of segments has a constant distribution of values and various values by requirement. Number of Comments is better than Priority to apply the actual search-based algorithm.

@@

@@

\caption{EX1 - Profit Comparison for each dataset}
\label{fig:DatasetProfit}
\end{figure*}

@@

At second experiment(EX2), we applied each algorithm to \textit{FIREFOX-III} dataset to see the correlation between cost and profit under the real estimated cost. And also, we expected to get the interesting range which have a great change as the limited budget are increased or decreased. For example, let's assume $R = {r_1, r_2, \ldots, r_5}$, $Cost = {10, 9, 8, 2, 1}$ and $Profit = {10, 9, 8, 2, 1}$. Then, if we see the maximum profit while decreasing the limited budget, we can verify that there is a peculiar point which have a great change of profit when the limited budget is 7. So, if possible, we wanted to verify a peculiar part on EX2.
\\

@@

\section{Result and Analysis}
All results of heuristic algorithms are averaged.\\

\textbf{RQ3}\textit{Which algorithms are well-suited for our datasets?}

At EX1, we applied two deterministic and three heuristic algorithms to four datasets and compared the averaged maximum profit to each other. Figure \ref{fig:DatasetProfit} shows the results of EX1. Each graph expresses the profit of five algorithms under the limited budget(= the estimated cost).

The SA has the smallest profit in most cases, except Figure \ref{fig:DatasetProfit}-(c). Although the SA started from a greedy solution, there is little difference between the result and a greedy solution. The profit of GA is bigger than SA and smaller than NSGA-II in every cases. So, the profit is high in order of NSGA-II, GA, then SA. The AHP has good performances for some cases. However, it has the lowest profit in \ref{fig:DatasetProfit}-(c).

The run time is also critical point to evaluate the performance. The run time of two deterministic algorithms takes just a few seconds. However, the run time of three heuristic algorithms takes more than 10 minutes. Although we consider that ILP used ILP solver, the run time of deterministic algorithms were much faster than heuristic algorithms.

Therefore, we can conclude that the ILP is well-suited for our datasets and also it is much faster than other heuristic algorithms.\\

To see the effect of different profit strategy, let's see the figure \ref{fig:DatasetProfit}-(b), (c), and (d) which are based on FIREFOX dataset but each of them has a different profit strategy. In the figure \ref{fig:DatasetProfit}-(b) and (d), GA has much bigger profit than SA and AHP has good performances enough to exceed NSGA-II. However, In the figure \ref{fig:DatasetProfit}-(c), GA has just little improvement from a greedy solution and AHP has the lowest profit among all algorithms. Therefore, we identified that the different profit strategy can affect the performance of algorithms.\\

One of the reasons to perform EX2 was that we wondered if there is a peculiar part in cost-profit graph. However, we cannot observe prominently peculiar part on EX2.\\

@@

\begin{table*}[t]
\caption{EX2 - Profit on each limited budget}
\begin{tabular}{@{}crrrrr@{}}
\toprule
\multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}The limited\\ budget\end{tabular}}} & \multicolumn{5}{c}{Algorithms}                                                                                                    \\ \cmidrule(l){2-6} 
\multicolumn{1}{c}{}                                                                              & \multicolumn{1}{c}{AHP} & \multicolumn{1}{c}{ILP} & \multicolumn{1}{c}{SA} & \multicolumn{1}{c}{GA} & \multicolumn{1}{c}{NSGA-II} \\ \midrule
100,000 & 14472.21303& \textbf{14530.92923}& 13787.94014& 13916.62496& 14359.51809\\
120,000 & 16798.95935& \textbf{16845.48739}& 16269.28033& 16440.60658& 16746.14339\\
140,000 & 18948.34660& \textbf{18979.35023}& 18553.36746& 18706.04924& 18906.95215\\
160,000 & 20906.31785& \textbf{20934.94744}& 20559.69749& 20656.69427& 20873.08535\\
180,000 & 22683.10701& \textbf{22718.92665}& 22332.52554& 22449.04724& 22651.51132\\
200,000 & 24343.18852& \textbf{24369.86106}& 23894.25792& 24054.60654& 24281.04096\\
220,000 & 25881.18360& \textbf{25901.23028}& 25425.18545& 25565.45349& 25804.51079\\
240,000 & 27305.09756& \textbf{27324.51067}& 26790.58789& 26987.08126& 27214.27095\\
260,000 & 28626.58769& \textbf{28653.54334}& 28161.56720& 28293.21833& 28556.63614\\ \bottomrule
\end{tabular}
\label{table:ParetoFront}
\end{table*}
